---
title: "Crossword Puzzle Examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
   fig.width = 7, 
  out.width = '100%'
)
```


## Example 1: Basic Crossword Puzzle

```{r setup, message=FALSE, warning=FALSE}
library(worrrd)
library(tidyverse)
library(rvest)
library(ggtext)
library(emoji)
```

Crossword puzzles are required to be intersecting, so it may not be possible to include every word that is provided.  Choosing the `method = 'optimal'` will place words in order of maximal overlap with every other word, while `method = 'random'` will place words in a random order and may therefore result in more words being excluded from the puzzle.

```{r}
df <- 
  dplyr::tribble(
    ~word, ~clue,
    "dog", "Bark. Bark. Bark.",
    "cat", "Purrr",
    "horse", "Neighhhhh",
    "frog", "Ribbit Ribbit",
    "cow", "Moooooooo",
    "fox", "Nee Nee Nee (What does the ____ say?)",
    "sheep", "Bleat",
    "snake", "Hissss",
    "duck", "Quack",
    "bird", "Chirp"
  )
ex1 <- crossword(words = df$word, clues = df$clue, r = 40, c = 40)
plot(ex1, solution = T, clues = T)
```


## Example 2:  Math Problem Puzzle

Here we create math problems randomly, and then use the `english` package to automatically convert the numeric solutions into words that are then placed into the puzzle.

```{r}
library(english)
df <- dplyr::tibble(
  n1 = round(20 * runif(20)),
  n2 = round(20 * runif(20)),
  sign = sample(c("+", "-"), 20, replace = T),
  problem = paste(n1, sign, n2),
  solution = purrr::map_dbl(problem, ~eval(parse(text = .x))),
  solution_text = as.english(solution)
) %>%
  dplyr::filter(
    solution > 0,
    !duplicated(solution)
  )

ex2 <- crossword(words = df$solution_text, clues = df$problem, r = 50, c = 50)
plot(ex2, clues = T, solution = T, title = "Math Makes Me Cross")
```