---
title: "Wordsearch Examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
   fig.width = 7, 
  out.width = '100%'
)
```


## Example 1: Basic Wordsearch

Let's start off with creating a basic wordsearch.

```{r setup, message=FALSE, warning=FALSE}
library(worrrd)
library(tidyverse)
library(rvest)
library(ggtext)
library(emoji)
```

```{r}
words <- c("dog", "cat", "horse", "frog", "cow", "fox")
ex1 <- wordsearch(words, r = 10, c = 10)
plot(ex1, solution = T)
```

## Example 2: Emoji Clues

Now we'll introduce the `clues` parameter.  This is useful if you want to show something different than the actual word in the search list.  In this example we'll use the same list of words, but show the emojis as the `clues`.  Credit to [Emil Hvitfeldt](https://www.hvitfeldt.me/blog/real-emojis-in-ggplot2/) for how to put emojis into a ggplot.

```{r}
# Function to convert emoji to link
emoji_to_link <- function(x) {
  x %>%
    emoji::emoji() %>%
    paste0("https://emojipedia.org/emoji/", .) %>%
    rvest::read_html() %>%
    rvest::html_nodes("tr td a") %>%
    .[1] %>%
    rvest::html_attr("href") %>%
    paste0("https://emojipedia.org/", .) %>%
    xml2::read_html() %>%
    rvest::html_node('div[class="vendor-image"] img') %>%
    rvest::html_attr("src")
}
link_to_img <- function(x, size = 25) {
  paste0("<img src='", x, "' width='", size, "'/>")
}

# Create wordsearch data
df <- 
  dplyr::tibble(
    words = c("dog", "cat", "horse", "frog", "cow", "fox")
  ) %>%
  dplyr::mutate(
    url = map_chr(words, slowly(~emoji_to_link(.x), rate_delay(1))),
    clues = link_to_img(url)
    )

# Build + plot
ex2 <- wordsearch(words = df$words, clues = df$clues)
plot(ex2, solution = T, title = "Emojis", legend_size = 4)   # set legend_size to force ggtext
```


## Example 3:  Math Problems

You can get creative with the `clues`.  In this example we'll create a wordsearch that requires the user to complete the math problems before finding the words.

```{r}
math <- dplyr::tribble(
  ~problem,  ~solution,
  "2 + 2",   "four",
  "5 + 3",   "eight",
  "9 - 4",   "five",
  "1 + 0",   "one",
  "2 + 1",   "three",
  "5 + 5",   "ten",
  "6 - 6",   "zero"
)

ex3 <- wordsearch(words = math$solution, clues = math$problem)
plot(ex3, solution = T, title = "Math is Fun")
```

## Example 4:  More Math Problems

Here we create more math problems randomly, and then use the `english` package to automatically convert the numeric solutions into words that are then placed into the puzzle.

```{r}
library(english)
df <- dplyr::tibble(
  n1 = round(20 * runif(20)),
  n2 = round(20 * runif(20)),
  sign = sample(c("+", "-"), 20, replace = T),
  problem = paste(n1, sign, n2),
  solution = purrr::map_dbl(problem, ~eval(parse(text = .x))),
  solution_text = as.english(solution)
) %>%
  dplyr::filter(
    solution > 0
  )

ex4 <- wordsearch(words = df$solution_text, clues = df$problem, r = 15, c = 15)
plot(ex4, solution = T, title = "Math is Really Fun", legend_size = 4)
```
