---
title: "Word search examples"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
   fig.width = 7, 
  out.width = '100%'
)
```


## Example 1: Basic Word search

Let's start off with creating a basic word search.

```{r setup, message=FALSE, warning=FALSE}
library(worrrd)
library(tidyverse)
library(rvest)
library(ggtext)
library(emoji)
```

```{r}
words <- c("dog", "cat", "horse", "frog", "cow", "fox")
ex1 <- wordsearch(words, r = 10, c = 10)
plot(ex1, solution = TRUE)
```

## Example 2: Animal Sounds

Now we'll introduce the `clues` parameter.  This is useful if you want to show something different than the actual word in the search list.  In this example we'll use the same list of words, but we'll use the sounds the animals make as the `clues`.

```{r}
clues <- c("Bark", "Meow", "Neigh", "Ribbit", "Moo", "Nee Nee Nee")
ex2 <- wordsearch(words = words, clues = clues)
plot(ex2, solution = T, title = "Animal Sounds", legend_size = 4)   # set legend_size to force ggtext
```

<!-- ## Example 2: Emoji Clues -->

<!-- Now we'll introduce the `clues` parameter.  This is useful if you want to show something different than the actual word in the search list.  In this example we'll use the same list of words, but show the emojis as the `clues`.  Credit to [Emil Hvitfeldt](https://www.hvitfeldt.me/blog/real-emojis-in-ggplot2/) for how to put emojis into a ggplot. -->

<!-- ```{r} -->
<!-- # Function to convert emoji to link -->
<!-- emoji_to_link <- function(x) { -->
<!--   x %>% -->
<!--     emoji::emoji() %>% -->
<!--     paste0("https://emojipedia.org/emoji/", .) %>% -->
<!--     rvest::read_html() %>% -->
<!--     rvest::html_nodes("tr td a") %>% -->
<!--     .[1] %>% -->
<!--     rvest::html_attr("href") %>% -->
<!--     paste0("https://emojipedia.org/", .) %>% -->
<!--     xml2::read_html() %>% -->
<!--     rvest::html_node('div[class="vendor-image"] img') %>% -->
<!--     rvest::html_attr("src") -->
<!-- } -->
<!-- link_to_img <- function(x, size = 25) { -->
<!--   paste0("<img src='", x, "' width='", size, "'/>") -->
<!-- } -->

<!-- # Create wordsearch data -->
<!-- df <- -->
<!--   dplyr::tibble( -->
<!--     words = c("dog", "cat", "horse", "frog", "cow", "fox") -->
<!--   ) %>% -->
<!--   dplyr::mutate( -->
<!--     url = map_chr(words, slowly(~emoji_to_link(.x), rate_delay(1))), -->
<!--     clues = link_to_img(url) -->
<!--     ) -->

<!-- # Build + plot -->
<!-- ex2 <- wordsearch(words = df$words, clues = df$clues) -->
<!-- plot(ex2, solution = T, title = "Emojis", legend_size = 4)   # set legend_size to force ggtext -->
<!-- ``` -->


## Example 3:  Math Problems

You can get creative with the `clues`.  In this example we'll create a word search 
that requires the user to complete the math problems before finding the words.

```{r}
math <- dplyr::tribble(
  ~problem,  ~solution,
  "2 + 2",   "four",
  "5 + 3",   "eight",
  "9 - 4",   "five",
  "1 + 0",   "one",
  "2 + 1",   "three",
  "5 + 5",   "ten",
  "6 - 6",   "zero"
)

ex3 <- wordsearch(words = math$solution, clues = math$problem)
plot(ex3, solution = TRUE, title = "Math is Fun")
```

## Example 4:  More Math Problems

Here we create more math problems randomly, and then use the `english` package to automatically convert the numeric solutions into words that are then placed into the puzzle.

```{r}
library(english)
n_words <- 20
dat <- dplyr::tibble(
  n1 = round(n_words * runif(n_words)),
  n2 = round(n_words * runif(n_words)),
  sign = sample(c("+", "-"), n_words, replace = T),
  problem = paste(n1, sign, n2),
  solution = purrr::map_dbl(problem, ~eval(parse(text = .x))),
  solution_text = as.english(solution)
) %>%
  dplyr::filter(
    solution > 0,           # only solutions > 0
    !duplicated(solution)   # no duplicates allowed
  )
ex4 <- wordsearch(words = dat$solution_text, clues = dat$problem, r = 15, c = 15)
plot(ex4, solution = TRUE, title = "Math is Really Fun", legend_size = 4)
```

## Example 5: Custom Shapes (⚠️ Experimental)

Wait, what?  You want to make it in the shape of a banana?  I mean, that's kinda weird... but why not!

_Note:_ A new, random search is generated each time you submit the command. If the 
words do not fit well, try regenerating the word search.

```{r wordsearch-banana}
library(cowplot)
banana <- "https://upload.wikimedia.org/wikipedia/commons/9/96/Tux_Paint_banana.svg"
words <- c("banana", "apple", "grapes", "orange", "pear", "kumquat")
ex5 <- wordsearch(words, r = 20, c = 20, image = banana)
plot(ex5, solution = TRUE)
```

Or try overlaying your image with the search.

```{r wordsearch-banana-overlay}
cowplot::ggdraw() +
  cowplot::draw_image(banana) +
  cowplot::draw_plot(plot(x, solution = TRUE))

```


## Example 6: Custom Shapes (⚠️ Experimental)

This lion was hungry.  Can you find the antelope he ate?

```{r wordsearch-lion}
lion <- "https://us.123rf.com/450wm/miceking/miceking1506/miceking150601500/40903456-stock-vector-lion-silhouette.jpg"
ex6 <- wordsearch("antelope", r = 40, c = 40, image = lion)
plot(ex6, solution = TRUE, puzzle_size = 2)
```


